\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-26 OaklandSubmission/intro.tex

\subsubsection*{Cryptogaphic-cost awareness} \mpc compiler is aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators, and their corresponding
inter-conversion gates. Based on these costs, the compiler, given a
source program, automatically picks arithmetic or boolean
representations for different parts of the program, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol using a combination of
arithmetic and boolean circuits, while the programmer remains
oblivious of all the low-level cryptographic details. Our evaluation
shows that the performance of the
protocols automatically generated by the \tool compiler is comparable
to or better than the custom, specialized protocols developed in the
previous work. Indeed, \tool is the first such cryptographic-cost
aware compiler.

>>>>

\subsubsection*{Cryptogaphic-cost awareness} \tool compiler is aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators, and their corresponding
inter-conversion gates. Based on these costs, the compiler, given a
source program, automatically picks arithmetic or boolean
representations for different parts of the program, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol using a combination of
arithmetic and boolean circuits, while the programmer remains
oblivious of all the low-level cryptographic details. Our evaluation
shows that the performance of the
protocols automatically generated by the \tool compiler is comparable
to or better than the custom, specialized protocols developed in the
previous work. Indeed, \tool is the first such cryptographic-cost
aware compiler.
